### 2020-12-17 README.Rmd
oops

```r
devtools::install_github("svmiller/stevetemplates")
```

@@

tic()
create_dyadyears() %>%
  # Add Gleditsch-Ward codes
  add_gwcode_to_cow() %>%
  # Add GML MIDs 
  add_mids %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()

>>>>

```r
devtools::install_github("svmiller/peacesciencer")
```

@@

tic()
create_dyadyears() %>%
  # Add Gleditsch-Ward codes
  add_gwcode_to_cow() %>%
  # Add GML MIDs 
  add_mids() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()
